### 2017-12-01 manuscript.rmd
Made Supplementary headers for phylogenetic signal and vertical evolution

```{r median_cont, echo=F, message=F, warning=F, fig.width=6.5, fig.height=7, fig.cap= "Stochastic character map of median depth of species"}
depth_value = depth_median
depthmap <- contMap(dpruned_tree, depth_value, plot=F) %>% setMap(colors=c("cyan","blue","black"))
plot(depthmap)
```

>>>>

#####Vertical Habitat Evolution
```{r median_cont, echo=F, message=F, warning=F, fig.width=6.5, fig.height=7, fig.cap= "Stochastic character map of median depth of species"}
depth_value = depth_median
depthmap <- contMap(dpruned_tree, depth_value, plot=F) %>% setMap(colors=c("cyan","blue","black"))
plot(depthmap)
```

#####Phylogenetic Signal
